Naturalness in U(1) extensions of the MSSM

### 2014-12-18 paper/e6ssm-tuning-paper.tex
rephrased first paragraph of results section.  Hopefully reads better now.

\documentclass[preprint,amsmath,amssymb,aps,superscriptaddress,prd,showpacs,floatfix,nofootinbib]{revtex4-1}

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}
\usepackage{hyperref}
\usepackage{footmisc}
% macros
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\ba}{\begin{eqnarray}}
\newcommand{\ea}{\end{eqnarray}}
\newcommand{\SuperField}[1]{\hat{#1}}

 \renewcommand\footnotelayout{\fontsize{10}{9}\selectfont}

\allowdisplaybreaks
%\nofiles
% For draft, uncomment to avoid huge spaces
\raggedbottom
%
\begin{document}

@@

% DH:: I'm not sure if this is worth including? I've put a disclaimer in the
% text, as well.
\begin{figure}[h]
\begin{center}
\resizebox{!}{10cm}{%
\includegraphics{mssm_higgs_tuning.png}}
\caption{Scatter plot of fine tuning in the MSSM as a function of
the lightest Higgs mass, $m_{h_1}$, for the cut-off scales (from 
bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV.}
\label{Fig:mssmhiggstuning}
\end{center}
\end{figure}
To illustrate this, in Fig.~\ref{Fig:mssmstoptuning} we show the
variation in fine tuning when we scan over the stop masses and mixing,
with $500 \textrm{ GeV} \leq m_{Q_3},m_{u_3}\leq 10\textrm{ TeV}$ and
$-3810\textrm{ GeV}\leq A_t\leq -20\textrm{ GeV}$, for $M_X=20$ TeV,
$50$ TeV and $100$ TeV.  The remaining parameters we fix such that at
$M_{SUSY}$ they have the values $\mu=-97.5$ GeV, $B=-84.8$ GeV,
$M_1=92.1$ GeV, $M_2=95.9$ GeV, $M_3=352$ GeV, $A_b=-117.9$ GeV,
$A_\tau=-7.8$ GeV, $m_{L_i}=400$ GeV, $m_{e_i}=204$ GeV,
$m_{Q_{1,2}}=438$ GeV, $m_{u_{1,2}}436$ GeV and $m_{d_i}=438$ GeV
($i=1,2,3$). By making this choice for the remaining parameters we
ensure that fine tuning due to each is small, so that we avoid washing
out the fine tuning impact of the stops when the tuning is
small \footnote{For models in which the spectrum is heavier, when the
  stop masses become very small the fine tuning reaches a lower bound
  imposed by other heavier parameters.} as can be the case when the
stop masses are less than 1 TeV.  Note that the Higgs mass is also
allowed to vary over the scan, as shown in
Fig.~\ref{Fig:mssmhiggstuning}.  However this tuning only really
becomes large for very large stop masses.  On the other hand if the
cuttoff is increased then stop masses of several TeV can result in
tuning of [insert] as shown in Fig.~\ref{Fig:mssmstoptuning}.\\ \\

>>>>

\documentclass[preprint,amsmath,amssymb,aps,superscriptaddress,prd,showpacs,floatfix]{revtex4-1}

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}
\usepackage{hyperref}

% macros
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\ba}{\begin{eqnarray}}
\newcommand{\ea}{\end{eqnarray}}
\newcommand{\SuperField}[1]{\hat{#1}}
\allowdisplaybreaks
%\nofiles
% For draft, uncomment to avoid huge spaces
\raggedbottom
%
\begin{document}

@@

% DH:: I'm not sure if this is worth including? I've put a disclaimer in the
% text, as well.
\begin{figure}[h]
\begin{center}
\resizebox{!}{10cm}{%
\includegraphics{mssm_higgs_tuning.png}}
\caption{Scatter plot of fine tuning in the MSSM as a function of
the lightest Higgs mass, $m_{h_1}$, for the cut-off scales (from 
bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV.}
\label{Fig:mssmhiggstuning}
\end{center}
\end{figure}
To illustrate this, in Fig.~\ref{Fig:mssmstoptuning} we show the variation in fine
tuning when we scan over the
stop masses and mixing, with $500 \textrm{ GeV} \leq
m_{Q_3},m_{u_3}\leq 10\textrm{ TeV}$ and $-3810\textrm{ GeV}\leq
A_t\leq -20\textrm{ GeV}$, for $M_X=20$ TeV, $50$ TeV and $100$ TeV.
The remaining parameters we fix such that at $M_{SUSY}$ they have the values $\mu=-97.5$ GeV, $B=-84.8$ GeV,
$M_1=92.1$ GeV, $M_2=95.9$ GeV, $M_3=352$ GeV, $A_b=-117.9$ GeV, $A_\tau=-7.8$ GeV, $m_{L_i}=400$ GeV, $m_{e_i}=204$ GeV,
$m_{Q_{1,2}}=438$ GeV, $m_{u_{1,2}}436$ GeV and $m_{d_i}=438$ GeV ($i=1,2,3$). By making this choice for the 
remaining parameters we ensure that fine tuning due to each is small, allowing us to see the fine tuning
impact of the stops for stop masses of less than 1 TeV. For models in which the spectrum is heavier the fine tuning
reaches a lower bound imposed by other heavier parameters as the stop masses become very small.
Note that the Higgs mass is also allowed to vary over the scan, as shown in 
Fig.~\ref{Fig:mssmhiggstuning}.
However this tuning only really becomes large for very large stop
masses.  On the other hand if the cuttoff is increased then stop masses of
several TeV can result in tuning of [insert] as shown in
Fig.~\ref{Fig:mssmstoptuning}.\\ \\
